
\newpage
\addcontentsline{toc}{section}{Список литературы}

\begin{thebibliography}{9}


\bibitem{bron1973algorithm} Bron, C. Algorithm 457: finding all cliques of an undirected graph. /
C. Bron, J. Kerbosch // Communications of the ACM. 1973. Т. 16. №. 9. С. 575-577.

\bibitem{coleman1983estimation} Coleman, T. F. Estimation of sparse Jacobian matrices and graph coloring blems. / T. F. Coleman, J. J. Moré // SIAM journal on Numerical Analysis. 1983. Т. 20. №. 1. С. 187-209.

\bibitem{day1986computational} Day, W. H. E. Computational complexity of inferring phylogenies by compatibility. / W. H. E. Day, D. Sankoff // Systematic Biology. 1986. Т. 35. №. 2. С. 224-229. 

\bibitem{erdios1935combinatorial} Erdios, P. A combinatorial problem in geometry. / P. Erdios, G. Szekeres // Compositio mathematica. 1935. Т. 2. С. 463-470.

\bibitem{harary1957procedure} Harary, F. A procedure for clique detection using the group matrix. / F. Harary, I. C. Ross // Sociometry. 1957. Т. 20. №. 3. С. 205-215.

\bibitem{kuhl1984combinatorial} Kuhl, F. S. A combinatorial algorithm for calculating ligand binding. / F. S. Kuhl, G. M. Crippen, D. K. Friesen // Journal of Computational Chemistry. 1984. Т. 5. №. 1. С. 24-34.

\bibitem{lagarias1992keller} Lagarias, J. C. Keller’s cube-tiling conjecture is false in high dimensions. / J. C. Lagarias, P. W. Shor // Bulletin of the American Mathematical Society. 1992. Т. 27. №. 2. С. 279-283.

\bibitem{luce1949method} Luce, R. D. A method of matrix analysis of group structure. / R. D. Luce, A. D. Perry //Psychometrika. 1949. Т. 14. №. 2. С. 95-116.

\bibitem{muegge2001small} Muegge, I. Small molecule docking and scoring. / I. Muegge, Rarey M. Small, //Reviews in computational chemistry. 2001. Т. 17. С. 1-60.

\bibitem{national1995mathematical} National Research Council Mathematical challenges from theoretical/computational chemistry. / National Research Council and others // National Academies Press, 1995.

\bibitem{rhodes2003clip} Rhodes, N.  CLIP: similarity searching of 3D databases using clique detection. / Rhodes, Nicholas, Willett, Pete, // Journal of chemical information and computer sciences. 2003. Т. 43. №. 2. С. 443-448.

\bibitem{robson2001finding} Robson, J. M. Finding a maximum independent set in time O (2n/4). / J. M. Robson // Technical Report 1251-01, LaBRI, Université Bordeaux I, 2001.

\bibitem{samudrala1998graph} Samudrala, R. A graph-theoretic algorithm for comparative modeling of protein structure1. / R. Samudrala, J. Moult // Journal of molecular biology. 1998. Т. 279. №. 1. С. 287-302.

\bibitem{spirin2003protein} Spirin, V. Protein complexes and functional modules in molecular networks. / V. Spirin, L. A. Mirny //Proceedings of the National Academy of Sciences. 2003. Т. 100. №. 21. С. 12123-12128.

\bibitem{tarjan1977finding} Tarjan, R. E. Finding a maximum independent set. / R. E. Tarjan, A. E. Trojanowski // SIAM Journal on Computing. 1977. Т. 6. №. 3. С. 537-546.

\end{thebibliography}
